TG2 Publications

### 2025-08-18 papers.qmd
fixed broken links

* Royston P, Sauerbrei W. Multivariable model-building: a pragmatic approach to regression analysis based on fractional polynomials for modelling continuous variables. John Wiley & Sons; 2008. [https://www.wiley.com/en-us/Multivariable+Model+-+Building%3A+A+Pragmatic+Approach+to+Regression+Anaylsis+based+on+Fractional+Polynomials+for+Modelling+Continuous+Variables-p-9780470028421](Link)
<br> *Presents a pragmatic, structured approach to multivariable model building, where emphasis is on modeling continuous variables using fractional polynomials. Focuses on interpretability and clinical relevance of statistical models.*.

@@

* Boer C de. A Practical Guide to Splines revised edn. Springer: New York, 2001. [https://link.springer.com/book/9780387953663](Link)
<br> *Covers spline-based methods in detail, offering practical advice for incorporating flexible functional forms into regression models*.

* Hastie T, Tibshirani R.. Generalized Additive Models. Chapman & Hall/CRC: New York, 1990. [https://www.routledge.com/Generalized-Additive-Models/Hastie-Tibshirani/p/book/9780412343902](Link)
<br> *Introduces foundational concepts in additive modeling, balancing statistical theory with illustrative applied examples*.

>>>>

* Royston P, Sauerbrei W. Multivariable model-building: a pragmatic approach to regression analysis based on fractional polynomials for modelling continuous variables. John Wiley & Sons; 2008. [Link](https://www.wiley.com/en-us/Multivariable+Model+-+Building%3A+A+Pragmatic+Approach+to+Regression+Anaylsis+based+on+Fractional+Polynomials+for+Modelling+Continuous+Variables-p-9780470028421)
<br> *Presents a pragmatic, structured approach to multivariable model building, where emphasis is on modeling continuous variables using fractional polynomials. Focuses on interpretability and clinical relevance of statistical models.*.

@@

* Boer C de. A Practical Guide to Splines revised edn. Springer: New York, 2001. [Link](https://link.springer.com/book/9780387953663)
<br> *Covers spline-based methods in detail, offering practical advice for incorporating flexible functional forms into regression models*.

* Hastie T, Tibshirani R.. Generalized Additive Models. Chapman & Hall/CRC: New York, 1990. [Link](https://www.routledge.com/Generalized-Additive-Models/Hastie-Tibshirani/p/book/9780412343902)
<br> *Introduces foundational concepts in additive modeling, balancing statistical theory with illustrative applied examples*.
